Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-26 02_Paper/paper.tex
worked on section 2.1
Solve merge issue section LS

\subsection{Quality check in production} % Basic books (find summarize) basic concepts

The quality control of production processes and products is one part of the general quality management
and contains the measures and activities needed to fulfill the quality requirements \cite{illes2017new}.
According to Illés, currently there are three established tools and methods of quality control \cite{illes2017new}:
The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
The SPC is used to monitor the production process using recorded data values for the quality characteristics and to indicate any significant changes
in the quality characteristics in the production process \cite{selvamuthu2018introduction}. It can take place before and after a manufacturing process
as off-line SPC or implemented in the manufacturing process as in-line SPC.
With SPC, large batches can be checked, but it is only possible, if the variance of the process and product parameters is small enough,
to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
Auditing, in this case especially product and process auditing, is the most fundamental quality control technique. 
Product and process auditing is the independent examination of product and process quality to provide information. This is executed by
an independent auditor, based on sampling, or checking records. But the auditor is just reporting incorrect processes or products. The required adapting is done by others \cite{fox1993quality}.
Both statistical methods and hundred percent controls can be applied as an audit tool.
Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Statistical methods are faster as hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
if the variance of the product quality is to high.
The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
by involving all departments of the organization \cite{illes2017new}.
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, 
precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.

@@

Predictive analytics discover according to Delen and Damirkan explanatory and predictive patterns which represents 
the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
This offers a wide range of applications. In the context of industrial or production enviroments, this includes in the areas of Processes, Products and Machines and Assets for example 
predictive maintenance, product design or optimization of routing and scheduling \cite{krauss2019machine}. 
Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
etablished quality control methods, in terms of speed, accuracy and time delay.
So far, only in exceptional cases in the literature is a combination of predictive analytics and quality control found \cite{aumi2012model, ritter1992neue}. With regard to general approaches to the use of predictive analytics,
for example in the form of machine learning in quality prediction, there is a lack in the literature. 
Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}. 
The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
the collection and processing of the data from the process parameters in continous and a few different ML algorithms are used for prediction, 
in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
In addition, it is described in detail how the collected data was collected, prepared and processed.

\AP{
Predictive analytics as concepts. Implementation in production
\begin{itemize}
       \item Predictive Maintenance
       \item Scheduling
       \item Other
\end{itemize}       
If happens to be something with P.A. Quality Check
\begin{itemize}
       \item	Predictive analytics in production focusing in QA
       \item	Existing approaches and methods
\end{itemize}      
Note: Ideal is to find a gap in the literature, that proves why do we do it and why it is important
}

@@

\begin{figure}
       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
       \caption{Robot arm movement patterns. We show the movement of the 
                cell's robot arm, its grippers and an encoding of the overall
                position in the system. The changes in the grip flag are triggered,
                when the gripper opens or closes. Zero indicates an open, while
                one indicates a closed gripper. The position flags marks the state
                of the cell's arm. 0 means the black disk is in store,
                one that the black disk is in the gate, two that the white disk
                is in store and three that the white disk is located in gate.
             }
\label{fig:robot_pos_cell}
\end{figure}

\AP{ @Moritz: Why is the figure 2 whithin the area of the Demozelle section?}

\section{Methods} %3/4 Page

Data  is collected from the demonstration cell and analyzed.

\subsection{Measurement}
\DSt{
- what is this section about?
}

\subsection{Machine Learning}
We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as Random forests in the task of
quality prediction.

@@

\subsection{Classifier optimization and testing}\label{sec:ml_exp}
The robot's position at disc drop is marked in 
Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
framed as a classification task. The input vectors which we feed into our
classifiers consists of the arm positions at the disc drops for both
discs in three dimensions, as well as the largest recorded belt speed
of all three belts. The interpretation of the quality measurement is 
used as the training target. It can be good or bad which we encode as 
zero and one.

@@

- Connection problem between devices
- Missing tags  
- Interpretation of data: preprocessing   
   - What data is relevant?
- Data sample size
- ML implementation @Moritz

>>>>

\subsection{Quality check in production} \label{sec:qcp} % Basic books (find summarize) basic concepts

The quality control of production processes and products is one fundamental part of the general quality management. It contains the measures and activities needed to fulfill specific quality requirements \cite{illes2017new}.
According to Illés, there are three established tools and methods of quality control \cite{illes2017new}:
The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes
in the quality characteristics in the production process \cite{selvamuthu2018introduction}. This method can take place right before and/or after a manufacturing process and be implemented as an "off-line" or "in-line" SPC.
\AP{@Lennart, last sentence is still quite confising to me}

The biggest advantage of working with SPC is that large batches can be checked without major time impact on the QC process, however, this would be only possible if the variance of the process product parameters is small enough, to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.

\AP{100\% method is not introduced}

Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique. This method is executed by
an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation. In a further step, the findings would be later corrected by other than the auditor \cite{fox1993quality}.

Both statistical methods and hundred percent controls can be applied as an audit tool.

Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.

While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Statistical methods are faster as \AP{as "or" "than"} hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
if the variance of the product quality is to high.
The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
by involving all departments of the organization \cite{illes2017new}.
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, 
precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.

@@

According to Delen and Damirkan, predictive analytics (PA) consist on unravel the inherent relationships, if any, between data input and output by using data and mathematical techniques \cite{delen2013data}.

PA offers a wide range of applications, and it can be implemented as long as there is enough data available. By conosidering industrial and production environment, PA would be a great asset due to the high flexibility and high amound of data available comming from processes, single machines or cells, producs, and others. Some commmon industrial applications of PA at the industry are focused products (design and optimization), machine (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.

Applications that combines PA with QC might be a great improvement in the quality control process because it is an improvement compared with the earlier mentioned methods \ref{sec:qcp}, in terms of speed, accuracy and time delay.

The outcome of an explorative literature review on this matter, shows that the findings that combines PA and QC are very scarce in literature. This could be in great part, due to the novelty of the area \cite{aumi2012model, ritter1992neue}. Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.

Based on an explorative literature review on this matter, the short outcome is that the findings that combines PA and QC are very scarce in literature. This could be in great part, due to computer power limitations in early researchs and the recent increase of ML applications on this area  \cite{aumi2012model, ritter1992neue}. Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.

\AP{
       - Introduce research question
       - why do we do it?
       - what do we expect to find or prove
       - the motivation is clear

The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
the collection and processing of the data from the process parameters in continous and a few different ML algorithms are used for prediction, 
in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
In addition, it is described in detail how the collected data was collected, prepared and processed.

\AP{Last paragraph goes in intro}

@@

\section{Machine Learning Methods} %3/4 Page

We compare Support Vector Machines (SVM), Multilinear Perceptrons
\cite{bishop2006pattern} as well as Random forests in the task of
quality prediction.

@@

\subsection{Classifier optimization and testing}\label{sec:ml_exp}

\begin{figure}
       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
       \caption{Robot arm movement patterns. We show the movement of the 
                cell's robot arm, its grippers, and the encoding of the overall
                position in the system. The changes in the grip flag are triggered,
                when the gripper opens or closes. Zero indicates an open, while
                one indicates a closed gripper. The position flags marks the state
                of the cell's arm. 0 means the black disk is in store,
                one that the black disk is at the gate, two that the white disk
                is in store and three that the white disk is located at the gate.
             }
\label{fig:robot_pos_cell}
\end{figure}

The robot's position at disc drop is marked in 
Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
framed as a classification task. The input vectors which we feed into our
classifiers consists of the arm positions at the disc drops for both
discs in three dimensions, as well as the largest recorded belt speed
of all three belts. The interpretation of the quality measurement is 
used as the training target. It can be good or bad which we encode as 
zero and one.

@@

- Connection problem between devices
   - Network connection
   - Device restriction: SIM4000, SIEMENS. 
   - Server Timestamp syncr.
- Interpretation of data: preprocessing
   - What data is relevant?
   - Missing data tags: modifying PLC and robot code to have tags -> key point
        - Without label we cannot use supervised ML methods
- Dataset size
- ML implementation @Moritz
